### 2013-03-19 doc/final_report/design.tex
Added new preprocessor sections

>>>>

The preprocessor module is used to annotate and analyse new papers once they 
have been uploaded by the user via the web interface. The preprocessor is designed 
as a daemon which uses pyinotify to hook into the operating system and monitor a directory 
for new papers that have been uploaded. As new papers are detected within the upload directory, 
they are placed into a process queue and the preprocessor analyses them on a first in first out basis.

When a paper is taken from the queue, a series of processes are run upon it to prepare 
it for storage in the database.

\subsubsection{Conversion}

\subsubsection{Sentence Splitting}

\subsubsection{SAPIENTA Annotation}

\subsubsection{Type Analysis}
